---
title: "Hello R"
author: "Brandon Montenegro Melendez"
date: "Data 2401"
output: 
  html_document: 
    highlight: tango
    theme: yeti
---

### Load packages 1

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. The variables included in the dataframe are dataset, x, and y. 

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Plot of the dino dataset from the Datasaurus Dozen.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
Correlation coefficient tells us there is no correlation between the x and the y variables. 

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Plot of the star dataset from the Datasaurus Dozen. 
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
Correlation coefficient tells us there is no correlation between the x and the y variables. 

### Exercise 4

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Plot of the circle dataset from the Datasaurus Dozen.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

Correlation coefficient tells us there is no correlation between the x and the y variables. 

### Exercise 5

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")


```

Plots of all datasets from the Datasaurus Dozen.

```{r cor-all datasets}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)

```

Correlation coefficient tells us there is no correlation between the x and the y variables in any of these datasets.